Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-04 causal-bandit/icml-2015/discussion.tex
Redoing discussion

@@

@@

\section{Future Open Questions}

\subsection{General graphs with known structure but latent variables}
In this case, some queries will be non-identifiable. The corresponding actions can be immediately added to the set $A$ prior to collecting any data. We can then use the same algorithm as in the case where there are no latent variables, except that we will have to use the more general do-calculus rather than simply adjusting for the parents to write the expression for each action in terms of observational data.

\subsection{Graphs with partially or unknown structure}

@@

@@

\end{itemize}
\section{Conclusion}

>>>>

Both our general causal model algorithm and algorithm for parallel bandits are adaptive reward estimators.

@@

% Non-observable variables? 
% Currently assume all P_a are available (implied by observablity)
%   - do calculus' identifability
%   - non-ident variables into infinite variance case.

%

@@

\subsection{Open Questions}

\paragraph{General graphs with known structure but latent variables}
In this case, some queries will be non-identifiable. The corresponding actions can be immediately added to the set $A$ prior to collecting any data. We can then use the same algorithm as in the case where there are no latent variables, except that we will have to use the more general do-calculus rather than simply adjusting for the parents to write the expression for each action in terms of observational data.

\paragraph{Graphs with partially or unknown structure}

@@

\item Unknown in general case - e.g., like algorithm 1

@@

\end{itemize}
